### 2016-07-26 main text/draft.tex
After thesis

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
%\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{slantsc}
\usepackage[latin1]{inputenc}   
\usepackage[T1]{fontenc}   
\usepackage[finnish]{babel}

@@

\begin{abstract} 
Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to data from M101 and
found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
galaxies: individual: M31, M101, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.01.tex}

@@

\import{../sections/}{method0.01.tex}

@@

\import{../sections/}{data0.01.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\import{../sections/}{results0.01.tex}
\import{../sections/}{R10.01.tex}
\import{../sections/}{R20.01.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}

We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
Self-organizing maps both cluster data and show relative distance between the clusters. 
We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.

Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
These anti-correlations are insignificant when the full dataset is considered.
The most probable reason for PAHs to anti-correlate with optical emission line and RHI is a harder radiation field.
This makes the size of H {\sc II} regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.

PAHs in clustered data also show an anti-correlation with stellar mass.
We discussed the possibility that higher stellar mass might destroy PAHs;
however, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.

In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
We found the relative similarity between M31 regions by varying the size of the networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
Two-dimensional networks provide us with a more complete picture of the data.
We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
In that network region 10 blends more with other regions and only shows differences with the data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
Increasing the dimension of the data and the number of regions would yield more reliable networks.
In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.

\section*{ACKNOWLEDGMENTS}
The authors thank Dr A.\ Tammour for useful comments. 
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
%\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{slantsc}
\usepackage[T1]{fontenc}

@@

\begin{abstract} 
Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to data from M101 and
found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
galaxies: individual: M31, M101, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.02.tex}

@@

\import{../sections/}{method0.02.tex}

@@

\import{../sections/}{data0.02.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\import{../sections/}{results0.02.tex}
\import{../sections/}{R10.02.tex}
\import{../sections/}{R20.02.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Summary}
\label{sec: summary}

We present the results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
Self-organizing maps both cluster data and show relative distance between the clusters. 
We utilized the method to find hidden subgroups in the data as well as to find relations between those groups.

Using smaller-sized self-organizing maps, we clustered M31 data into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
These anti-correlations are insignificant when the full dataset is considered.
The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.

PAHs in clustered data also show an anti-correlation with stellar mass.
We discussed the possibility that higher stellar mass might destroy PAHs;
however, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.
The reason behind the observed anti-correlation between PAH features and stellar mass needs further investigation, which requires mid-infrared PAH observations for more regions in M31.

In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
We found the relative similarity between M31 regions by varying the size of the networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
Two-dimensional networks provide us with a more complete picture of the data.
We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
Region 10, which is located in the bulge of M31, always becomes isolated in the networks, except when we  used only PAH data to create a network.
In that network region 10 blends more with the other regions and is only differentiated from region 8, which is located inside the inner ring of M31.
These results suggest that the PAHs in all 10 regions have almost the same properties.

We introduced self-organizing maps as a method that can be used to predict various quantities based on the relative positions of the regions in the networks.
For regions that lack the observational data for some quantities (e.g. PAH emission), SOMs can be used to extrapolate the unobserved quantities.
Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.

The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
Increasing the dimension of the data and the number of regions would yield more reliable networks.
Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
The method described in this work can be used to select target regions for PAH observations with that facility.

\section*{ACKNOWLEDGMENTS}
The authors thank Dr.s D.\ Stock and A.\ Tammour for useful comments. 
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}

### 2016-07-26 sections/V0.01/R10.01.tex
After thesis

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

@@

      Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to show more similarities to each other.
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings.
       The SOM shows that this region has a completely different input values than the others.
       Comparing raw data for regions shows that most of the input values for region 10 are much higher than the other regions, which is the main reason of its isolation.
        The region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.

@@

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths, or with most of the other quantities.
        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves. 
        For example region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
        This region could be part of scatter for these correlations, but with 6 regions in the dataset it is hard to have a concrete conclusion.

        For the remaining PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity.
        These fluxes correlate with SPIRE emission, but to a lesser extent than for data from all regions.
        Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier: Region 6. 
        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
        Strong anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.

        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
        Second, is the possible effect of observing apertures.
        If the observed regions are located near the edge of H {\sc II} regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features' underlying continuum emission is from the H {\sc II} regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, a higher stellar mass decreases PAH emission.
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation. Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity).
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

@@

        Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities to each other. %%present? show? represent? have?
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings.
       The SOM shows that this region has a completely different input values than the others.
       Comparing raw data for regions shows that most of the input values for region 10 are much higher than the other regions, which is the main reason of its isolation.
        The region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.

@@

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m, SPIRE 250 to 500~$\mu$m~emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes at other wavelengths, or with most of the other quantities.
        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\mathrm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities reappear. 
        For example region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
        This region could be part of scatter for these correlations, but with 6 regions in the dataset it is hard to have a concrete conclusion.

        For the PAH fluxes except 12.0 and 12.7~$\mu$m in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
        These PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier: Region 6. 
        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.

        Strong anti-correlations between 6.2 to 11.3~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
        Second, is the possible effect of observing apertures.
        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Jones15,Lu14,Calapa14,Bendo08,Haas02}, a higher stellar mass decreases PAH emission.
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation. Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an \hii~region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
